---
title: "Assignment 3"
author: "Patrick Ha"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Complete 15/15

```{r echo = FALSE}
getwd()
```


# Question 1 

M.S 5.54 - pg 215

**a. What is the probability of observing an interarrival time of at least 2 minutes?**

\[ 2 \text{ minutes} = 120 \text{ seconds} \] \[ P(Y > 120) = \int_0^{\infty}\frac{e^{-y/\beta}}{\beta}dy = \int_{120}^{\infty}\frac{e^{-y/95}}{95}dy = \frac{1}{95}\Big[-95e^{-y/95}\Big]_{120}^{\infty} = -\frac{1}{95}\Big[0-e^{-120/95}\Big] = .2876 \]

\[P(Y>120) = .2876 \


**b. Data for a sample of 267 interarrival times are saved in the PHISHING file. Do the data appear to follow an exponential distribution with b = 95?**

We understand that a mean of an exponential distribution is beta or 1/lambda = 95. Standard deviation of an exponential distribution is 1.lambda = 95 (sd = sqrt(var)).

```{r}
phishing = read.csv("PHISHING.csv")
mean(phishing$INTTIME)
sd(phishing$INTTIME)
```

Based on the calculated data we can conclude that the mean and standard deviation of an exponential distribution is 95.52377 and 91.53912 respectively.



# Question 2 

M.S. 5.56 pg 215

**a. Find the mean and variance of the maximum flood level over a 4-year period for the Susquehanna River.**

