---
title: 'Ass 2: Template'
author: "Patrick Ha "
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = TRUE)
```

# Questions 15/15 COMPLETED

## Q 1 - Completed

Condition: Match P(Correct|Expert) = .9212 P(Correct|Novice) =.7455

a)Given a pair of matched prints, what is the probability that an expert will fail to identify the match?

**\[P(Incorrect|Novice) = P (Correct`|Novice) = 1-.9212 = .0788\]**


**There is a .0788 probability that an expert will fial to idenify the match given a pair of matched prints**


b)Given a pair of matched prints, what is the probability that a novice will fail to identify the match?

\[P(Incorrect|Novice) = P(Correct'|Novice) = 1-.7455 = .2545 \]

**There is a .2545 probability that a novice will fail to identify the mathc given a pair of matched prints.**

c)Suppose that a pair of matched prints are presented to a randomly selected study participant and the participant fails to identlify the match. Is the participant more likely to be an expert or a novice?

**Assume the study incldued 10 participants, 5 experts and 5 novices.**

\[ P(Expert) = 5/10 = .5, P(Novice) = 5/10 = .5\] \[ P(Expert|Incorrect) = \frac{P(Incorrect|Expert)P(Expert)}{P(Incorrect|Expert)P(Expert) + P(Incorrect|Novice)P(Novice)} \] \[P(Expert|Incorrect) = \frac{(.0788)(.5)}{(.0788)(.5) + (0.2545)(.5)} = .2364 \] \[P(Novice|Incorrect) = 1-P(Expert|Incorrect) = 0.7636 \]

**The participant is more likely to be a novice**


## Q 2 - Completed

a)Given the athlete is a user, find the probability that a drug test for test for testosterone will yield a positive result. 

\[P(+|User) = 50/100 =.5\]'

b)Given the athlete is a nonuser, find the probability that a drug test for testosterone will yield a negative result.

\[P(-|Nonuser) = 891/900 =.99\]

c)If an athlete tests positive for testosterone, use Bayes' Rule to find the probability that the athlete is really doping. 

\[P(User|+) = P(+|User)P(User)/P(+) \]
\[P(User|+) = (.5)(.1)/(.059)= .8475\]

**Given an athlete tests positive for testosterone, there is a .8475 probability that the athlete is really doing.**

## Q 3- Completed
The multiplicative ruler
\[n_1n_2n_3n...n_k\] For example:
You have three choices of pasta: bow-tie, spaghetti, rigatoni, lasagna

You have two choices of sauce: Alfredo, pesto

You have four choices of toppings: chicken, sausage, meatballs, shrimp.


For each distinct variable combination:

1) bow-tie, Alfredo, chicken

2) bow-tie, Alfredo, sausage

3) bow-tie, Alfredo, meatballs

4) bow-tie, Alfredo, shrimp

5) bow-tie, pesto, chicken

6) bow-tie, pesto, sausage

7) bow-tie, pesto, meatballs

8) bow-tie, pesto, shrimp

9) spaghetti, Alfredo, chicken

10) spaghetti, Alfredo, sausage

11) spaghetti, Alfredo, meatballs

12) spaghetti, Alfredo, shrimp

13) spaghetti, pesto, chicken

14) spaghetti, pesto, sausage

15) spaghetti, pesto, meatballs

16) spaghetti, pesto, shrimp

17) lasagna, Alfredo, chicken

18) lasagna, Alfredo, sausage

19) lasagna, Alfredo, meatballs

20) lasagna, Alfredo, shrimp

21) lasagna, pesto, chicken

22) lasagna, pesto, sausage

23) lasagna, pesto, meatballs

24) lasagna, pesto, shrimp

3 x 2 x 4 = 24

**This could be reiterated with other numbers of choices in groupings to create the multiplicative rule. As seen by the different combinations listed out, each crust can have each sauce, and then each sauce per that crust can have a different topping. Thus, multiplying each different variable gives the total number of combinations possible.**

## Q 4- Completed

The permutations rule:

Given N elements, select a sample of n where each oreder creates a distinct combinations:

Imagine you have six numbers and six slots that all need to be filled, and each slot must have a different digit.

\[______\]

So you fill the first slot with a number. When you fill the first slot, none of teh numbers have been selected yet, so you can pick from six different options.

\[[6]_ _ _ _ _\]

Now that you've filled the first slot with the nubmer, you only have five options of numbers left to select. So when you select the next, there are only five choices.

\[[6][5]_ _ _ _\]

The next will only have four opttions, since there are only four digits left:

\[[6][5][4] _ _ _\]

And so on, until you've run out of slots to fill. 

\[[6][5][4][3][2][1]\]

if you pick numbers in different orders every time, you'll get 6x5x4x3x2x1 = 720 different ways to select numbers, or N!.

Digits that aren’t used:

When you only have three slots, you still have six digits to choose from when you make the first selection:

\[[6]_ _\]

Now that you’ve selected one, you have five digits to choose from when you make the second selection:

\[[6][5]_\]

When you finally make the third selection, you’ll only have four digits to choose from:

\[[6][5][4]\]

Thus, you divide the combinations formula by (N-n)!, to represent the number of options you didn’t choose, aka 3x2x1 on this occasion. Dividing N! by (N-n)! removes the leftover options you didn’t select.

6x5x4x3x2x1 –> 6x5x4 because we used (N-n)!.

Thus, when selecting from N elements for a sample of n, the rule is this:

\[ N! / (N-n)! \]

## Q 5- Completed

The partitions rule:

Given N elements, partition them into k sets where the number of elements in k sets adds up to N

Imagine you have six numbers and six slots that all need to be filled, and each slot must have a different digit.

\[_ _ _ _ _ _\]

So you fill the first slot with a number. When you fill the first slot, none of the numbers have been selected yet, so you can pick from six different options.

\[[6]_ _ _ _ _\]

Now that you’ve filled the first slot with the a number, you only have five options of numbers left to select. So when you select the next, there are only five choices.

\[[6][5]_ _ _ _\]

The next will only have four options, since there are only four digits left:

\[[6][5][4] _ _ _\]

And so on, until you’ve run out of slots to fill.

\[[6][5][4][3][2][1]\]

If you pick numbers in different orders every time, you’ll get 6x5x4x3x2x1 = 720 different ways to select numbers, or N!.

Partitioning into groups

Lets say you only have three slots to fill instead of six because you’re creating the first group of three.

Before you pick the first digit, you have three slots empty to fill:

\[_ _ _\]

Before you pick the second digit, you have two slots empty to fill:

\[X _ _\]

Before you pick the third digit, you have one slots empty to fill:

\[X X _\]

When you think of the amount of limited spots you have to fill, such as three slots, each time you pick a slot, you have less slots to place the next number because order doesn’t matter; {_ X } and {X _} are not distinct. The number of slots available before you choose each selection can be represented as n! or 3x2x1.

However, since you have multiple groups until all elements from N are used n_k = N, we’ll have to do this multiple times for each individual group, making it:

\[n_1!n_2!n_3!...n_k!\]

Finally, you divide the number of total event combinations by the number of combinations avaible in groupings to get:

\[\frac{N!}{n_1!n_2!n_3!...n_k!}\]

## Q 6- Completed

The combinations rule:

Given N elements, choose n for a sample where order dosen't matter.

Imagine you have six numbers and six slots that all need to be filled, and ecah slot must have a different digit.

\[______\]

So you fill the first slot with a number. When you fill the first slot, none of the numbers have been selected yetm so you can pick from six different options. 

\[[6]_____\]

Now that you've filled the first slot with a number, you only have five options of numbers left to select. 

So when you select the next, there are only five choices.

\[[6][5]____\]

The next will only have four options, since there are only four digits left:

\[[6][5][4]___\]

And so on, until you're run out of slots to fill. 

\[[6][5][4][3][2][1]\]

If you pick numbers in different orders every time, you'll get 6! = 720 different ways to select numbers, or N!.

Adjusting for order:

lets say you only have three slots in fill istead of six. 

before you pick the first digit, you have three slots empty to fill:

\[___\]

Before you pick the second digit, you have two sltos empty to fill:

\[X__\]

Before you pcik the third digit, you have one slots empty to fill:

\[XX_\]

When you think of the amoung of limited spots you have to fill, such as three slots, each time you pick a slot, you have less slots to place the next number because order dosen't matter. The number of slots available before you choose each selection can be represented as n!

Digits that aren't used: 

When you only have three slots, you still have six digits to choose from when you make the first selection: 

\[[6]__\]

Now that you've selected one, you have five digits to choose fromw hen you amke the second selection:

\[[6][5]_\]

When you finally make the third selection, you'll only have four digits to choose from:

\[[6][5][4]\]

Therefore, you will divide the combinations formula by (N-n)!, to represent the number of options you didn't choose. In this occasion diving N! by (N-n)! removes the leftover options you didn't select. 

6x5x4x3x2x1 -> 6x5x4 because we used (N-n)!

Finally, addint on ! because order dosen't matter results in:

\[N! / (n!(N-1)!)\]

## Q 7- Completed

a) Verify that the probabilities for y in the table sum to 1. 

\[\sum Y = .09 + .30 + .37 + .20 + .04 = 1\]

b) Find the probability that three or four of the homes in the sample have a dust mite level that exceeds 2 ug/g.


\[P (Y = 3,4) = P(Y = 3) + P(Y=4) = .20 + .04 = .24\]

c) Find the probability that fewer than two homes in the sample have a dust mite level that exceeds 2 ug/g

\[P(Y < 2) = P(Y = 0) + P(Y=1) = .09 + .30 = .39\]

## Q 8- Completed

a) Show that the properties of a probability distribution for a discreate random variable are satisfied. 

b) Find P (Y >= 10).

\[ P(Y >= 10)= P(Y=10) + P(Y = 11) + ... + P(Y = 20) = .02 +.02 +.02 + .02 + .01 + .01 + .01 + .01 + .01 + .005 +.005 = .14 \] \[\mu_{Y} = E\sum Y = (0).17 + (1).10 + (2).11 + (3).11 + (4).10 + (5).10 + (6).07 + (7).05 + (8).03 + (9).02 + (10).02 +(11).02 +(12).02 + (13).02 + (14).01 + (15).01 + (16).01 + (17).01 + (18).01 + (19).005 + (20).005 = 4.655\]

\[\sigma^2_{Y} = E\sum Y^2 - \mu_{Y}^2 \]

\[E \sum Y^2 = (0^2).17 + (1^2).10 + (2^2).11 + (3^2).11 + (4^2).10 + (5^2).10 + (6^2).07 + (7^2).05 + (8^2).03 + (9^2).02 + (10^2).02 +(11^2).02 +(12^2).02 + (13^2).02 + (14^2).01 + (15^2).01 + (16^2).01 + (17^2).01 + (18^2).01 + (19^2).005 + (20^2).005 = 41.525 \]


c) Find the mean and variance of Y.
\[ \mu_{Y}^2 = 4.655^2 = 21.6690 \]

\[ E \sum Y^2 - \mu_{Y}^2 = 41.525 - 21.6690 = 19.856 \]


d) Give an interval that will contai the value of Y with a probability of at least .75. 

According to Chebyshev's rule, At least 75% of the data will fall within 2 standard deviations fo the mean. 


\[ \sigma = \sqrt{\sigma^2} = \sqrt{19.856} = 4.456007 \] \[ \mu \pm 2\sigma = 4.655 \pm 2*4.456007 = -4.257014, 13.56701 \]


## Q 9- Completed

a) Find P(Y = 10)

\[ {n \choose y} = {25 \choose 10} = 25!/10!(25-10)! = 3268760 \]

\[ p^yq^{n-y} = .7^{10}(1-.7)^{25-10} = 4.053211e{-10}\] \[ P(Y=10) = {n \choose y}p^yq^{n-y} = {25 \choose 10}.7^{10}(1-.7)^{25-10} = 3268760 * 4.053211e{-10} = 0.001324897 \]



b) Find P(Y <= 5)

\[ P(Y<=5) = P(Y=0) + P(Y=1) + P(Y=2) + P(Y=3) + P(Y=4) + P(Y=5) \]

\[P(Y=0) = {n \choose y}p^yq^{n-y} =\dfrac{25!}{0!25!} .7^{0}(.3)^{25} = 1 * 8.472886e{-14} = 8.472886e{-14}\] \[P(Y=1) = {n \choose y}p^yq^{n-y} =\dfrac{25!}{1!24!} .7^{1}(.3)^{24} = 25 * 1.977007e{-13} = 4.942518e{-12}\] \[P(Y=2) = {n \choose y}p^yq^{n-y} =\dfrac{25!}{2!23!} .7^{2}(.3)^{23} = 300 * 4.613016e{-13} = 1.383905e{-10}\] \[P(Y=3) = {n \choose y}p^yq^{n-y} =\dfrac{25!}{3!22!} .7^{3}(.3)^{22} = 2300 * 1.07637e{-12} = 2.475651e{-9}\] \[P(Y=4) = {n \choose y}p^yq^{n-y} =\dfrac{25!}{4!21!} .7^{4}(.3)^{21} = 12650 * 2.511531e{-12} = 3.177086e{-8}\]

\[P(Y=5) = {n \choose y}p^yq^{n-y} =\dfrac{25!}{5!20!} .7^{5}(.3)^{20} = 53130 * 5.860239e{-12} = 3.113545e{-7}\]

\[P(Y<=5) = 8.472886e{-14} + 4.942518e{-12} + 1.383905e{-10} + 2.475651e{-9} + 3.177086e{-8} + 3.113545e{-7} = 3.457444e-07 \]

c) Find the mean U and standard deviation o for Y.

\[ \mu = np = 25(.7) = 17.5 \]

\[ \sigma^2 = npq = 25(.7)(1-.7) = 5.25 \] \[ \sigma = \sqrt{\sigma^2} = \sqrt{5.25} = 2.291288 \]


d) Interpret the results, part c.

**According to the data on average, about 17.5 people out 25 students are pursing an engineering degree are foreign. Based on the standard deviation the number varies by 2.29 above or below the mean, so around 15.2 to 19.8 students are typically foreign nationals out of a sample of 25. **

## Q 10 - Completed

a) What is teh probability that exactly 5 trains are assinged to each of the 10 tracks?

\[\dfrac{n!}{y_1!y_2!y_2!...y_k!} \] \[\dfrac{50!}{(5!)^{10}} = 4.912046e+43 \]

Since all the tracks are randomly selected and each track should have five trains:

\[(p_1)^{Y_1}(p_2^{Y_2}...(p_{10})^{Y_{10}} = (.10)^{5*10} \] \[\dfrac{50!}{(5!)^{10}}(.10)^{50} = 4.912046e-7\]

b) A track is considered underutilized if fewer than 2 trains are assigned to the track during the day. Find the probability that Track #1 is underutilized. 

\[P(Y_i=0) = \dfrac{50!}{0!50!}(.10)^{0}(.90)^{50} = 0.005153775 \]

\[P(Y_i=1) = \dfrac{50!}{1!49!}(.10)^{1}(.90)^{49} = 0.02863208 \]

\[P(Y_i<2)= 0.005153775 + 0.02863208 = 0.03378586 \]

## Q 11- Completed

a) Give a formula for the probability distribution of Y. 
\[P(elsewhere) = 1-.45-.15 = .4 \]

\[ pq^{y-1} = (.40)(.60)^{y-1} \]


b) What is E(Y)? Interpret the result

\[ E(Y) = \mu = \frac{1}{p} = \frac{1}{.4} = 2.5 \]

Based on the result of E(Y) on average, you would need to interview 2.5 consumers to find one wwho gives a resason other than information on the product's label or packaging for why they consider the product "green".

c) Find P(Y = 1)

\[ P(Y=1) = (.40)(.60)^{1-1} = .40 \]

d) Find P(Y > 2) 

\[ P(Y=1) = (.40)(.60)^{1-1} = .40 \] \[ P(Y=2) = (.40)(.60)^{1} = .24 \] \[P(Y>2) = 1-P(Y=1)-P(Y=2) = 1-.40-.24=.36\]

## Q 12- Completed

a) In a random sample of 10 of the 209 facilities what is the expected number in the sample that treats hazardous waste on-site? Interpret this result

\[ E(Y) = \mu = \frac{nr}{N} = \frac{(10)(8)}{209} = 0.3827751 \]

Given a sample of 10 facilites, on average the number of facilites that will treat hazardous waste on site will be 0.3827751.

b) Find the probability that 4 of the 10 selected facilites treat hazardous waste on-site 

\[ P(Y=4) = \frac{{r \choose y}{{N-r} \choose {n-y}}}{{N \choose n}} = \frac{{8 \choose 4}{{209 - 8} \choose {10-4}}}{{209 \choose 10}} = 0.0001688459 \]

## Q 13- Completed

a) Find the variance of Y. 

\[ \sigma^2 = \lambda = .03 \]

b) Discuss the conditions that would make the researchers' Poisson assumption plausible 

**To make the Poisson assumption reasiionable casualties would need to be rare, occur indenpendenly, and happend at a constant average rate over time. Events occur randomly and singly, with the smae small probability for each vessel and time period. **


c) What is the probability that a deep-draft U.S. flag vessel will have no cassualties in a 3-year time period?

\[P(Y=0) = \frac{\lambda^ye^{-\lambda}}{y!} = \frac{.03^0e^{-.03}}{0!} = 0.9704455335\]


## Q 14- Completed

a) Find the value of c. 

\[\int_{-\infty}^{\infty} f(y) \,dy = \int_{0}^{1} c(2-y) \,dy = 2c - \int_{0}^{1} cy \,dy = 2c - \frac{y^2}{2}\Big]_0^1 = 2c - \frac{1}{2}c \]

\[ c = \frac{2}{3} \]


b) Find the cumulative distribution function F(y) 

\[ F(Y) = \int_{-\infty}^{y} f(t) \,dt = \int_{-\infty}^{y} \frac{2}{3}(2-y) \, dt = \frac{2}{3}\Big[ 2t-\frac{t^2}{2}\Big]_0^y = \frac{4y-y^2}{3}\]

c) Compute F(.4)

\[ \frac{4y-y^2}{3}= \frac{4(.4)-(.4)^2}{3} = .48\]

d) Compute P(.1 <= Y <= .6)

\[ P(.1) = \frac{4(.1)-(.1)^2}{3} = .13\]

\[ P(.6) = \frac{4(.6)-(.6)^2}{3} = .68\]

\[P(.1≤Y≤.6) = P(.6)-P(.1)=.68-.13=.55 \]

## Q 15 - Completed

a) Find the mean and variance of the amount of time in minutes the train is late

\[ \mu = E(Y) =\int_{-\infty}^{\infty} yf(y) \,dy = \int_{-5}^{5} y\frac{3}{500}(25-y^2) \,dy = \int_{-5}^{5} \frac{3y}{20} - \frac{3y^3}{500} \,dy = 0\]

The last steps can be simplified because they are odd functions, and integrating symmetrically around the axis will result in an area of zero. They are odd functions when compared to their parent graphs y=x and y=x^3.

\[\sigma^2 = E(Y^2) - \mu^2 \] \[ E(Y^2) = \int_{-\infty}^{\infty} y^2f(y) \,dy = \int_{-5}^{5} y^2\frac{3}{500}(25-y^2) \,dy = \frac{3}{500}\int_{-5}^{5} (25y^2-y^4) \,dy = 5\] \[\sigma^2 = 5 - 0^2 = 5 \]

b) Find the mean and variance of the amount of time in hours the train is late. 

\[ \mu = E(Y) =\int_{-\infty}^{\infty} \frac{y}{60}f(\frac{y}{60}) \,dy = \int_{-5}^{5} \frac{y}{60}\frac{3}{500}(25-(\frac{y}{60})^2) \,dy = \frac{3}{500}\int_{-5}^{5} (25(\frac{y}{60})-(\frac{y}{60})^3) \,dy = 0 \text{ hours}\] \[ \mu = E(Y^2) =\int_{-\infty}^{\infty} (\frac{y}{60})^2f(\frac{y}{60}) \,dy = \int_{-5}^{5} (\frac{y}{60})^2\frac{3}{500}(25-(\frac{y}{60})^2) \,dy = \frac{3}{500}\int_{-5}^{5} (25(\frac{y}{60})^2-(\frac{y}{60})^4) \,dy = 0.001388889 \text{ hours}^2\]

c) Find the mean and variance of the amount of time in seconds the train is late. 

\[\mu = E(Y) = 0 \text{ minutes} *60 \text{ seconds} = 0 \text{ seconds}\] \[\sigma^2 = 5 \text{ minutes} * 3600 \text{ seconds}^2 = 18000 \text{ seconds}^2\]

## Q 16- Completed


\[ F(Y) = \int_{-\infty}^{y} \frac{1}{{\sigma}\sqrt{2\pi}}e^{-\frac{(y-\mu)^2}{2\sigma^2}} \, dt \]


a) exceeding 45 milligrams per liter.

```{r}
round(1 - pnorm(45,50, 3.2), 4)
```

b) below 55 milligrams per liter.

```{r}
round(pnorm(55,50,3.2), 4)
```

c) between 51 and 52 milligrams per liter. 
```{r}
round(pnorm(52, 50, 3.2) - pnorm(51, 50, 3.2), 4) 
```

## Q 17 - Completed

a) Find the probability that the rating will fall between 500 and 700 points. 

\[ F(700) - F(500) = \int_{500}^{700} \frac{1}{{185}\sqrt{2\pi}}e^{-\frac{(y-605)^2}{2(185)^2}} \, dt = 0.4110396 \]

```{r}
round(pnorm(700, 605, 185) - pnorm(500, 605, 185), 4)
```

b) Find the probability that the rating will fall between 400 and 500 points.

\[ F(500) - F(400) = \int_{400}^{500} \frac{1}{{185}\sqrt{2\pi}}e^{-\frac{(y-605)^2}{2(185)^2}} \, dt = 0.1512568 \]

```{r}
round(pnorm(500, 605, 185) - pnorm(400, 605, 185), 4)
```

c) Find the probability that the rating will be less than 850 points. 

\[ F(850) = \int_{-\infty}^{850} \frac{1}{{185}\sqrt{2\pi}}e^{-\frac{(y-605)^2}{2(185)^2}} \, dt = 0.9073023 \]

```{r}
round(pnorm(850, mean = 605, sd = 185), 4)
```
d) Find the probability that the rating will be exceed 1,000 points.

\[ P(Y>1000) = \int_{1000}^{\infty} \frac{1}{{185}\sqrt{2\pi}}e^{-\frac{(y-605)^2}{2(185)^2}} \, dt = 0.016375 \]


```{r}
round(1 - pnorm(1000, 605, 185), 4) 
```


e) What rating will only 10% of the crash-tested cars exceed?


\[ .10 = \int_{y}^{\infty} \frac{1}{{185}\sqrt{2\pi}}e^{-\frac{(y-605)^2}{2(185)^2}} \, dt, x = 842.087 \]

```{r}
round(qnorm(0.90, mean = 605, sd = 185), 3)
```






