---
title: "Birthday"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Birthday}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753SPRINGHA)
```

## Question

The mathematical derivation of the probability that two ro more people in a class of size n have the same birthday.



### Mathematical Derivation 

The probability that at least two people share a birthday is:

$$P(n) = 1 - \frac{365!}{365^n \cdot (365-n)!}$$

Equivalently:

$$P(n) = 1 - \frac{P(365, n)}{365^n}$$

## Reformulation Using Logarithms

We will use the probability using lfactorial and lchoose

$$
P(a) = 1 - \exp\!\Big(\text{lfactorial}(n) + \text{lchoose}(365,n) - n \log(365)\Big)
$$


## Function

Body of the birthday function:

```{r}
birthday
```

## Function given

Using the function with the given r code.

```{r}
birthday(n = 20:25)
```

### Interpretation

According to the data in a class of 20 people, there is approximately a 41% chance of teh a shared birthday between 1 or 2 people. If there is a class of 23 people then the probability goes up to around 50% chance of people having a shared birthday. Lastly the 25 people have a 57% chance of having a shared birthday. 

