---
title: "MATH4753SPRINGHA"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MATH4753SPRINGHA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753SPRINGHA)
```

# Introduction
This vignette explains what the package does.


# Running the packages

# ntickets

This is the nticket fucntion. The purpose fo this fucntion is to help airlines determine how many tickets they shoudl sell for a flight. Given the number of actual seats on the plane. The propability that a ticketed passenger shows up; and the acceptable probability that the plane beocme truly overbooked.

```{r}

result<-ntickets()
result 
```


# myncurve

This package is teaching/visualization tool for the normal distribution. Where it will draw a normal curve with mean mu and standard deviation sigma. Then shades teh area from the far left up to a point a. Then it will compute the probability. Returns the parameters and teh calculated probability. 

```{r}
MATH4753SPRINGHA::myncurve(0,1,0)
```

# mycltb

The function mycltb() simulates the Central Limit Theorm using binomial distributions. 

```{r}
MATH4753SPRINGHA::mycltb(1,1,0.5)
```

# myBoot2

This fucntion uses the bootstrap method to estimate a confidence interval for any statistic(mean, median, etc)

```{r}
MATH4753SPRINGHA::myboot2(iter=10000,rnorm(20,10,4),fun="mean",alpha=0.05,cx=1.5)
```


# mybin

This function performs a binomial simulation

```{r}
MATH4753SPRINGHA::mybin(100, 10, 0.5)
```

# Birthday

The purpose of this function is to compute the probability that at least two people in a room share the same birthday, for a class of size n.

```{r}
MATH4753SPRINGHA::birthday(10)
```


#Github link

https://github.com/PatrickHeeHaw/AppliedStats.git



